Boundary Labeling for annotated documents

### 2018-03-23 LaTeX/Paper.tex
Paper: Added section 3.2 - GUI. Program: Source vertices are now always drawn. Updated incorrect comments.

%TODO: Screenshot nehmen und beschriften!

>>>>

The GUI of the program is very simplistic, as the main goal was to demonstrate the routing algorithm. As such, all customization options are located on the control panel above the drawing area, which contains the text, leaders and annotations. (See also Fig.~\ref{fig:ProgWindow})

The control panel's first three options determine the font the program uses, whether it is bold or italicized and its size. The fourth and last option allows the selection of different routing algorithms. After changing any value, the program will automatically redraw the drawing area's contents, and re-do the routing.

The drawing area itself can't be interacted with, it only serves to display the algorithm's results.
\begin{figure}
	\captionsetup{justification=centering, margin=0.75cm}
	\centering
	\includegraphics[scale=0.75]{ProgramWindowAnnotated.png}
	\caption{<test>}
	\label{fig:ProgWindow}
\end{figure}
